\LARGE{{\bf{Gravitational Wave Signals from Multiple Hidden Sectors} \\ }}

### 2019-10-03 gwnnDraft02.tex
minor changes sects 4-5

%%%%%%%%%%%new definitions: 
\def\lsim{\mathrel{\rlap{\lower4pt\hbox{\hskip1pt$\sim$}}
  \raise1pt\hbox{$<$}}}
\def\gsim{\mathrel{\rlap{\lower4pt\hbox{\hskip1pt$\sim$}}
  \raise1pt\hbox{$>$}}}
\newcommand{\vev}[1]{ \left\langle {#1} \right\rangle }
\newcommand{\bra}[1]{ \langle {#1} | }
\newcommand{\ket}[1]{ | {#1} \rangle }
\newcommand{\ev}{ {\rm eV} }
\newcommand{\kev}{{\rm keV}}
\newcommand{\mev}{{\rm MeV}}
\newcommand{\gev}{{\mathrm GeV}}
\newcommand{\tev}{{\rm TeV}}
\newcommand{\mpl}{$M_{Pl}$}
\newcommand{\mw}{$M_{W}$}
\newcommand{\Ft}{F_{T}}
\newcommand{\Zparity}{\mathbb{Z}_2}
\newcommand{\BLambda}{\boldsymbol{\lambda}}
\newcommand{\met}{\;\not\!\!\!{E}_T}
\newcommand{\beq}{\begin{equation}}
\newcommand{\eeq}{\end{equation}}
\newcommand{\bea}{\begin{eqnarray}}
\newcommand{\eea}{\end{eqnarray}}
\newcommand{\nn}{\nonumber}
\newcommand{\hc}{\mathrm{h.c.}}
\newcommand{\eps}{\epsilon}
\newcommand{\bwt}{\begin{widetext}}
\newcommand{\ewt}{\end{widetext}}
\newcommand{\draftnote}[1]{{\bf\color{blue} #1}}
\newcommand{\cO}{{\cal O}}
\newcommand{\cL}{{\cal L}}
\newcommand{\cM}{{\cal M}}
%References  
\newcommand{\fref}[1]{Fig.~\ref{fig:#1}} 
\newcommand{\eref}[1]{Eq.~\eqref{eq:#1}} 
\newcommand{\aref}[1]{Appendix~\ref{app:#1}}
\newcommand{\sref}[1]{Section~\ref{sec:#1}}
\newcommand{\tref}[1]{Table~\ref{tab:#1}}
%\title{\LARGE{{\bf{Piled up gravitational waves:} \\
%\bf{Searching for new signals of $N$naturalness} }}}
\title{\LARGE{{\bf{Gravitational Wave Signals from Multiple Hidden Sectors} \\
}}}
\author{{\bf {Paul Archer-Smith, Dylan Linthorne, and Daniel Stolarski}}}
\affiliation{
Ottawa-Carleton  Institute  for  Physics,  Carleton  University,\\
1125  Colonel  By  Drive,  Ottawa,  Ontario  K1S  5B6,  Canada
}
\email{
PaulSmith3@cmail.carleton.ca \\
Dylan.linthorne@carleton.ca \\
stolar@physics.carleton.ca
}
\begin{abstract}
We explore the possibility of detecting gravitational waves generated by first order phase transitions in multiple hidden sectors. $N$naturalness is taken as a sample model that features multiple additional sectors, many of which undergo phase transitions that produce gravitational waves. We examine the cosmological history of this framework and determine the gravitational wave profiles generated. These profiles are checked against projections of next generation gravitational wave experiments, demonstrating that multiple hidden sectors can indeed produce unique gravitational wave signatures that will be probed by these future experiments. 
\end{abstract}
\maketitle
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

\section{Reheating N Sectors}
\label{sec:reheat}
%\begin{figure*}[tb]
%\centering
%\begin{minipage}[c]{\textwidth}
%\includegraphics[width=0.4\textwidth]{standardDecay.eps}
%\includegraphics[width=0.4\textwidth]{exoticDecay.eps}
%\end{minipage}
%\hfill
%\caption{Feynman diagrams for primary reheaton decays assuming $m_{\phi} \ll m_H$. The left decay is the primary decay for standard sectors ($\langle H\rangle\neq 0$), with $f$ representing all possible fermions. The right decay occurs in exotic sectors ($\langle H\rangle = 0$).
%}
%\label{fig:reheatonDecays}
%\end{figure*}
A key issue within $N$naturalness is how to predominantly gift energy density to our own sector so as to not be immediately excluded by cosmological constraints, particularly those from number of effective neutrinos ($N_{eff}$). Here we review the results of~\cite{Arkani-Hamed:2016rle}. Reheating occurs through the introduction a ``reheaton'' field. After inflation, the reheaton field possess the majority of the energy density of the Universe. Although this field can generically be either bosonic or fermionic, we reduce our scope to a scalar reheaton $\phi$. Our focus is primarily the production of gravitational waves from multiple sectors and a fermion reheaton does not change the scaling of the energy density of the exotic sectors and thus does not affect expected gravitational wave profiles.

In order to maintain the naturalness of our SM sector, the reheaton coupling is taken to be universal to every sector's Higgs. However, a large amount of the Universe's energy density must ultimately be deposited in our own sector for $N$naturalness to avoid instant exclusion. In order to accomplish this the decay width into each sector must drop as $\vert m_H\vert$ grows. If we insist that the reheaton is a gauge singlet that is both the dominant coupling to every sector's Higgs and lighter than the naturalness cutoff $\Lambda_H/\sqrt{N}$ then we construct a model that behaves as desired. 
The appropriate Lagrangian for a scalar reheaton $\phi$ is: 
\begin{equation}\label{eqn:nnLagrangian}
\cL_\phi \supset -a\phi\sum_i\vert H_i\vert^2 - \frac{1}{2}m^2_\phi \phi^2.
\end{equation}
Note that cross-quartic couplings of the form $\kappa\vert H_i\vert^2\vert H_j\vert^2$ that could potentially ruin the spectrum of $N$naturalness are absent, taken to be suppressed by a very small coupling. Effective Lagrangians for the two different types of sectors present in this theory can be obtained by integrating out of the Higgs bosons in every sector:
\begin{equation}\label{eqn:nnEffLag}
\begin{split}
\cL_\phi^{v \neq 0} &\supset C_1 a y_q\frac{v}{m_h^2}\phi q q^c,
\\
\cL_\phi^{v = 0} &\supset C_2 a \frac{g^2}{16\pi^2 m_H^2}\phi W_{\mu\nu}W^{\mu\nu},
\end{split}
\end{equation}
with $C_i$ representing numerical coefficients, $g$ the weak coupling constant, and $W^{\mu\nu}$ the SU$(2)$ field strength tensor.
Immediately from Eq. (\ref{eqn:nnEffLag}), we can see that the matrix element for decays into standard sectors is inversely proportional to that sectors Higgs mass, $\cM_{m_H^2 < 0} \sim 1/m_{h_i}$ (since $v\sim m_H$). 
%The Feynman diagram for this process is presented in Fig. \ref{fig:reheatonDecays}. 
The loop decay of $\phi \rightarrow \gamma\gamma$ is always sub-leading and can be neglected. It should be noted that as one goes to sectors with larger and larger vevs, the increasing mass of the fermions ($m_f \sim v_i \sim v_{SM}\sqrt{i}$) eventually leads to situations where the decay to two on-shell bottom or charm quarks is kinematically forbidden, $m_\phi < 2 m_q$. For sectors where this kinematic threshold is passed for charm quarks, the amount of energy in these sectors becomes so small that contributions to cosmological observables can be safely ignored. All in all, we end up with a decay width that scales as $\Gamma_{m_H^2<0} \sim 1/m_h^2$. Since we can expect energy density to be proportional to the decay width, $\frac{\rho_i}{\rho_{SM}} \approx \frac{\Gamma_i}{\Gamma_{SM}}$, this indicates that energy density of standard sectors falls:
\begin{equation}\label{eqn:edSS}
\rho_i \sim r_{s}\frac{\rho_{SM}}{i}
\end{equation} 
with $r_s$ being the ratio of the energy density of the first additional standard sector over the energy density of our sector.
For the exotic sectors, Eq.~(\ref{eqn:nnEffLag}) indicates a matrix element scaling $\cM_{m_H^2>0} \sim 1/m_{H_i}^2$ and is also loop suppressed. 
%As the Feynman diagram (Fig.~\ref{fig:reheatonDecays}) shows, the reheaton decays to exotic sectors are loop suppressed, 
This leads to a significantly lower energy density than the standard sectors. Both the decay width and energy density for these sectors scale as: 
\begin{equation}
\Gamma_{m_H^2>0} \sim \rho_i \sim 1/m_H^4 \sim 1/i^2.
\label{eq:reheat_exotic}
\end{equation}

As a final note, in this setup the reheating temperature of the SM, $T_{RH}$, has an upper bound on the order of the weak scale. If this bound is not observed, the SM Higgs mass would have large thermal corrections --- leading to the branching ratios into other sectors being problematically large~\citep{Arkani-Hamed:2016rle}. Thus we only consider relatively low reheating temperatures $\lesssim 100$ GeV.
Ultimately, after examining the gravitational wave case produced by standard $N$naturalness, we also consider a more generic parameterization where the reheating temperature of each sector is a free parameter and is in general uncorrelated with the Higgs mass parameter. This allows us to explore a broader model space with multiple dark sectors at a huge range of scales. For these models, the reheating mechanism remains unspecified.

@@

\subsection{Exotic Sector Contributions}
%The original $N$naturalness paper focused on the (stronger) $N_{eff}$ constraints from the additional standard sectors and ignored the exotic sectors altogether \cite{Arkani-Hamed:2016rle}; in contrast, we take the opposite approach. Since we're more interested in a more general scenario with multiple dark phase transitions, we focus in on whether zero vev sectors can dodge these $N_{eff}$ bounds. 
We begin by computing the constraints on exotic sectors; these are significantly weaker than those for standard sectors~\cite{Arkani-Hamed:2016rle}. 
%At high scales, these sectors feature 106.75 effective degrees of freedom at high energies: 72 from quarks,  12 from charged leptons, 6 from neutrinos, 16 from gluons, 2 from photons, 6 from W bosons (no longitudinal modes due to a no symmetry breaking), 4 from the higgs sector (again, no symmetry breaking leads to 3 additional modes), for a total of 118 degress of freedom. Scaling the fermionic contributions by $7/8$ gives us 106.75 effective relativistic degrees of freedom.  After the higgses freeze out, 4 degrees of freedom are lost; when the QCD phase transition occurs 35 bosonic degrees of freedom are gained while 72 fermionic are lost, leaving 56.75 effective degrees of freedom. 
At the time of photon decoupling ($T_\gamma \sim 0.39 \,\ev$) while the temperature of the exotic sectors is lower still. This means that for sectors with small and moderate $i$, we can use Eqs.~(\ref{eqn:exoticFM}) and~(\ref{eq:ith_pion_mass}) to see that the pions will be non-relativistic  leaving at most $11.25$ effective degrees of freedom per sector from photons and neutrinos.  For very large $i$, the pions can be much lighter, but those sectors also have very little energy in them in the standard reheating scenario. 
%Since all additional sectors are colder than our own, by the time photon decoupling occurs ($T_\gamma \sim 0.39 \,\ev$), the pions of all of these sectors will, in accordance with Eq.~(\ref{eqn:gmor}), have a much higher mass than the sector temperature and thus will have frozen out long before --- leaving at most $11.25$ effective degrees of freedom per sector from photons and neutrinos. \draftnote{Pions are not decoupled at BBN time, does this in any way affect the analysis?}
Coupling the number of effective degrees of freedom per sector with the energy density scaling of $\sim 1/m_H^4$ as in Eq.~(\ref{eq:reheat_exotic}) means that the zero vev sectors have small temperature ratios. Assuming a reheating temperature of $100$ GeV and a completely uniform distribution of sectors, the temperature of the first exotic sector is slightly more than $6\%$ of our sector at reheating. Applying Eq.~(\ref{eqn:DeltaNeff}) to this particular situation gives us:
\begin{equation}
\Delta N_{eff} = \sum_i \frac{4}{7}\left(\frac{11}{4}\right)^{4/3}g_{i} \left(\frac{(T_{RH_{E1}}/T_{RH})}{i^{1/2}}\right)^4 \sim 10^{-4},
\end{equation}     
with $T_{RH_{E1}}/T_{RH}$ being the ratio of the reheat temperatures of the 1st exotic sector and our own sector ($0.06$ in standard $N$naturalness with $r = 1$).  This sum is dominated by $i=1$, the sector with the lowest Higgs mass (and thus the most energy density) gives us a contribution of $\mathcal{O} (10^{-4})$ to $\Delta N_{eff}$. Evolving the sectors thermal histories forward in time to the recombination era gives us a slightly larger value, but still of order $\mathcal{O}(10^{-4})$, well under current CMB bounds. 
It should be noted that modifying the exotic sectors' structure (e.g. adjusting the exotic sectors to have a lower Higgs mass squared or clustering multiple hidden sectors close to the first exotic one) leads to a $\Delta N_{eff}$ contribution that is larger than the base $N$naturalness case. This increase is typically not excluded by current bounds, indicating a large degree of liberty in the structure and number of exotic hidden sectors.

@@

The generalization of possible reheating mechanisms mentioned in section~\ref{sec:reheat} --- where the reheating mechanism no longer depends on the Higgs' mass parameter of a given sector --- opens up a wide range of hidden sectors for study. Specifically, this allows mirror sectors with large Higgs vevs to be reheated to significant energy densities and thus produce gravitational waves with enough power to be detected. Crucially, despite this analysis being limited to mirror sectors with large Higgs masses, this analysis pertains to any strong, confining phase transition at high scales.
Since $N_{eff}$ constraints remain our strongest cosmological bounds for massive standard sectors, our starting point for exploring the limits of high transition temperatures is Eq.~(\ref{eqn:DeltaNeff}). Assuming heavy, standard sectors (with the only relativistic particles being photons and neutrinos) we can saturate the bounds of Eq.~(\ref{eqn:neffBounds}) and solve for the maximum temperature allowed for any number of sectors:
\begin{equation}\label{eqn:energyDensityAllowed}
\begin{split}
T_i &\sim 0.38 \,T_{SM} \,\,\,\,\, \mathrm{1}\,\, \mathrm{hidden}\,\, \mathrm{sector},
\\
T_i &\sim 0.25 \,T_{SM} \,\,\,\,\, \mathrm{5} \,\,\mathrm{hidden}\,\, \mathrm{sectors},
\\
T_i &\sim 0.21 \,T_{SM} \,\,\,\,\, \mathrm{10} \,\,\mathrm{hidden}\,\, \mathrm{sectors},
\\
T_i &\sim 0.12 \,T_{SM} \,\,\,\,\, \mathrm{100} \,\,\mathrm{hidden}\,\, \mathrm{sectors},
\end{split}
\end{equation}
where all the hidden sectors have the same temperature as one another.
Using these restrictions, we can examine the behaviour of standard sectors with a much larger vev than our own. In terms of the $N$naturalness framework, this means we can get an SFOPT for QCD if we look at sectors with $i$ greater than the cirtical index of Eq.~(\ref{eqn:critIndex}) where all the quark masses are above the QCD confinement scale as long as their temperatures are below the bounds presented here. 
 %of looking at various different sectors above the critical index, as mentioned in Sec.~\ref{sec:dQCD}. The signals for both the maximal case ($10^{16}$ limit) and several other high transition temperatures (involving sectors $i > 10^{10}$) scenarios are shown in Sec.~\ref{sec:gw}. \textcolor{yellow}{This assumes that only photons and neutrinos are relativistic? Yes.}

@@

\section*{Acknowledgement}

>>>>

%%%%%%%%%%%new definitions: 
\def\lsim{\mathrel{\rlap{\lower4pt\hbox{\hskip1pt$\sim$}}
  \raise1pt\hbox{$<$}}}
\def\gsim{\mathrel{\rlap{\lower4pt\hbox{\hskip1pt$\sim$}}
  \raise1pt\hbox{$>$}}}
\newcommand{\vev}[1]{ \left\langle {#1} \right\rangle }
\newcommand{\bra}[1]{ \langle {#1} | }
\newcommand{\ket}[1]{ | {#1} \rangle }
\newcommand{\ev}{ {\rm eV} }
\newcommand{\kev}{{\rm keV}}
\newcommand{\mev}{{\rm MeV}}
\newcommand{\gev}{{\mathrm GeV}}
\newcommand{\tev}{{\rm TeV}}
\newcommand{\mpl}{$M_{Pl}$}
\newcommand{\mw}{$M_{W}$}
\newcommand{\Ft}{F_{T}}
\newcommand{\Zparity}{\mathbb{Z}_2}
\newcommand{\BLambda}{\boldsymbol{\lambda}}
\newcommand{\met}{\;\not\!\!\!{E}_T}
\newcommand{\beq}{\begin{equation}}
\newcommand{\eeq}{\end{equation}}
\newcommand{\bea}{\begin{eqnarray}}
\newcommand{\eea}{\end{eqnarray}}
\newcommand{\nn}{\nonumber}
\newcommand{\hc}{\mathrm{h.c.}}
\newcommand{\eps}{\epsilon}
\newcommand{\bwt}{\begin{widetext}}
\newcommand{\ewt}{\end{widetext}}
\newcommand{\draftnote}[1]{{\bf\color{blue} #1}}
\newcommand{\cO}{{\cal O}}
\newcommand{\cL}{{\cal L}}
\newcommand{\cM}{{\cal M}}
%References  
\newcommand{\fref}[1]{Fig.~\ref{fig:#1}} 
\newcommand{\eref}[1]{Eq.~\eqref{eq:#1}} 
\newcommand{\aref}[1]{Appendix~\ref{app:#1}}
\newcommand{\sref}[1]{Section~\ref{sec:#1}}
\newcommand{\tref}[1]{Table~\ref{tab:#1}}
%\title{\LARGE{{\bf{Piled up gravitational waves:} \\
%\bf{Searching for new signals of $N$naturalness} }}}
\title{\LARGE{{\bf{Gravitational Wave Signals from Multiple Hidden Sectors} \\
}}}
\author{{\bf {Paul Archer-Smith, Dylan Linthorne, and Daniel Stolarski}}}
\affiliation{
Ottawa-Carleton  Institute  for  Physics,  Carleton  University,\\
1125  Colonel  By  Drive,  Ottawa,  Ontario  K1S  5B6,  Canada
}
\email{
Paul.Smith3@carleton.ca \\
Dylan.linthorne@carleton.ca \\
stolar@physics.carleton.ca
}
\begin{abstract}
We explore the possibility of detecting gravitational waves generated by first order phase transitions in multiple hidden sectors. $N$naturalness is taken as a sample model that features multiple additional sectors, many of which undergo phase transitions that produce gravitational waves. We examine the cosmological history of this framework and determine the gravitational wave profiles generated. These profiles are checked against projections of next generation gravitational wave experiments, demonstrating that multiple hidden sectors can indeed produce unique gravitational wave signatures that will be probed by these future experiments. 
\end{abstract}
\maketitle
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

\section{Reheating $N$ Sectors}
\label{sec:reheat}
%\begin{figure*}[tb]
%\centering
%\begin{minipage}[c]{\textwidth}
%\includegraphics[width=0.4\textwidth]{standardDecay.eps}
%\includegraphics[width=0.4\textwidth]{exoticDecay.eps}
%\end{minipage}
%\hfill
%\caption{Feynman diagrams for primary reheaton decays assuming $m_{\phi} \ll m_H$. The left decay is the primary decay for standard sectors ($\langle H\rangle\neq 0$), with $f$ representing all possible fermions. The right decay occurs in exotic sectors ($\langle H\rangle = 0$).
%}
%\label{fig:reheatonDecays}
%\end{figure*}
A key issue within $N$naturalness is how to predominantly gift energy density to our own sector so as to not be immediately excluded by cosmological constraints, particularly those from number of effective neutrinos ($N_{eff}$). Here we review the results of~\cite{Arkani-Hamed:2016rle}. Reheating occurs through the introduction a ``reheaton'' field. After inflation, the reheaton field possess the majority of the energy density of the Universe. Although this field can generically be either bosonic or fermionic, we reduce our scope to a scalar reheaton $\phi$. Our focus is primarily the production of gravitational waves from multiple sectors and a fermion reheaton does not change the scaling of the energy density of the exotic sectors and thus does not affect expected gravitational wave profiles.

In order to maintain the naturalness of our SM sector, the reheaton coupling is taken to be universal to every sector's Higgs. However, a large amount of the Universe's energy density must ultimately be deposited in our own sector for $N$naturalness to avoid instant exclusion. In order to accomplish this, the decay width of the reheaton into each sector must drop as $\vert m_H\vert$ grows. If we insist that the reheaton is a gauge singlet that is both the dominant coupling to every sector's Higgs and lighter than the naturalness cutoff $\Lambda_H/\sqrt{N}$, then we construct a model that behaves as desired. 
The appropriate Lagrangian for a scalar reheaton $\phi$ is: 
\begin{equation}\label{eqn:nnLagrangian}
\cL_\phi \supset -a\phi\sum_i\vert H_i\vert^2 - \frac{1}{2}m^2_\phi \phi^2.
\end{equation}
Note that cross-quartic couplings of the form $\kappa\vert H_i\vert^2\vert H_j\vert^2$ that could potentially ruin the spectrum of $N$naturalness are absent, taken to be suppressed by a very small coupling. Effective Lagrangians for the two different types of sectors present in this theory can be obtained by integrating out of the Higgs bosons in every sector:
\begin{equation}\label{eqn:nnEffLag}
\begin{split}
\cL_\phi^{v \neq 0} &\supset C_1 a y_q\frac{v}{m_h^2}\phi q q^c,
\\
\cL_\phi^{v = 0} &\supset C_2 a \frac{g^2}{16\pi^2 m_H^2}\phi W_{\mu\nu}W^{\mu\nu},
\end{split}
\end{equation}
with $C_i$ representing numerical coefficients, $g$ the weak coupling constant, and $W^{\mu\nu}$ the SU$(2)$ field strength tensor.
Immediately from Eq. (\ref{eqn:nnEffLag}), we can see that the matrix element for decays into standard sectors is inversely proportional to that sectors Higgs mass, $\cM_{m_H^2 < 0} \sim 1/m_{h_i}$ (since $v\sim m_H$). 
%The Feynman diagram for this process is presented in Fig. \ref{fig:reheatonDecays}. 
The loop decay of $\phi \rightarrow \gamma\gamma$ is always sub-leading and can be neglected. It should be noted that as one goes to sectors with larger and larger vevs, the increasing mass of the fermions ($m_f \sim v_i \sim v_{SM}\sqrt{i}$) eventually leads to situations where the decay to two on-shell bottom or charm quarks is kinematically forbidden, $m_\phi < 2 m_q$. For sectors where this kinematic threshold is passed for charm quarks, the amount of energy in these sectors becomes so small that contributions to cosmological observables can be safely ignored. All in all, we end up with a decay width that scales as $\Gamma_{m_H^2<0} \sim 1/m_h^2$. Since we can expect energy density to be proportional to the decay width, $\frac{\rho_i}{\rho_{SM}} \approx \frac{\Gamma_i}{\Gamma_{SM}}$, this indicates that energy density of standard sectors falls:
\begin{equation}\label{eqn:edSS}
\rho_i \sim r_{s}\frac{\rho_{SM}}{i}
\end{equation} 
with $r_s$ being the ratio of the energy density of the first additional standard sector over the energy density of our sector.
For the exotic sectors, Eq.~(\ref{eqn:nnEffLag}) indicates a matrix element scaling $\cM_{m_H^2>0} \sim 1/m_{H_i}^2$ and is also loop suppressed. 
%As the Feynman diagram (Fig.~\ref{fig:reheatonDecays}) shows, the reheaton decays to exotic sectors are loop suppressed, 
This leads to a significantly lower energy density than the standard sectors. Both the decay width and energy density for these sectors scale as: 
\begin{equation}
\Gamma_{m_H^2>0} \sim \rho_i \sim 1/m_H^4 \sim 1/i^2.
\label{eq:reheat_exotic}
\end{equation}

As a final note, in this setup the reheating temperature of the SM, $T_{RH}$, has an upper bound on the order of the weak scale. If this bound is not observed, the SM Higgs mass would have large thermal corrections --- leading to the branching ratios into other sectors being problematically large~\citep{Arkani-Hamed:2016rle}. Thus we only consider relatively low reheating temperatures $\lesssim 100$ GeV.

Ultimately, after examining the gravitational wave case produced by standard $N$naturalness, we also consider a more generic parameterization where the reheating temperature of each sector is a free parameter and is in general uncorrelated with the Higgs mass parameter. This allows us to explore a broader model space with multiple dark sectors at a huge range of scales. For these models, the reheating mechanism remains unspecified.

@@

\subsection{Exotic Sector Contributions}
%The original $N$naturalness paper focused on the (stronger) $N_{eff}$ constraints from the additional standard sectors and ignored the exotic sectors altogether \cite{Arkani-Hamed:2016rle}; in contrast, we take the opposite approach. Since we're more interested in a more general scenario with multiple dark phase transitions, we focus in on whether zero vev sectors can dodge these $N_{eff}$ bounds. 
We begin by computing the constraints on exotic sectors; these are significantly weaker than those for standard sectors~\cite{Arkani-Hamed:2016rle}. 
%At high scales, these sectors feature 106.75 effective degrees of freedom at high energies: 72 from quarks,  12 from charged leptons, 6 from neutrinos, 16 from gluons, 2 from photons, 6 from W bosons (no longitudinal modes due to a no symmetry breaking), 4 from the higgs sector (again, no symmetry breaking leads to 3 additional modes), for a total of 118 degress of freedom. Scaling the fermionic contributions by $7/8$ gives us 106.75 effective relativistic degrees of freedom.  After the higgses freeze out, 4 degrees of freedom are lost; when the QCD phase transition occurs 35 bosonic degrees of freedom are gained while 72 fermionic are lost, leaving 56.75 effective degrees of freedom. 
At the time of photon decoupling, $T_\gamma \sim 0.39 \;\ev$ while the temperature of the exotic sectors is lower. This means that for sectors with small and moderate $i$, we can use Eqs.~(\ref{eqn:exoticFM}) and~(\ref{eq:ith_pion_mass}) to see that the pions will be non-relativistic  leaving at most $11.25$ effective degrees of freedom per sector from photons and neutrinos.  For very large $i$, the pions can be much lighter, but those sectors also have very little energy in them in the standard reheating scenario. 
%Since all additional sectors are colder than our own, by the time photon decoupling occurs ($T_\gamma \sim 0.39 \,\ev$), the pions of all of these sectors will, in accordance with Eq.~(\ref{eqn:gmor}), have a much higher mass than the sector temperature and thus will have frozen out long before --- leaving at most $11.25$ effective degrees of freedom per sector from photons and neutrinos. \draftnote{Pions are not decoupled at BBN time, does this in any way affect the analysis?}
Coupling the number of effective degrees of freedom per sector with the energy density scaling of $\sim 1/m_H^4$ as in Eq.~(\ref{eq:reheat_exotic}) means that the zero vev sectors have small temperature ratios. Assuming a reheating temperature of $100$ GeV and a completely uniform distribution of sectors, the temperature of the first exotic sector is slightly more than $6\%$ of our sector at reheating. Applying Eq.~(\ref{eqn:DeltaNeff}) to this particular situation gives us:
\begin{equation}
\Delta N_{eff} = \sum_i \frac{4}{7}\left(\frac{11}{4}\right)^{4/3}g_{i} \left(\frac{(T_{RH_{E1}}/T_{RH})}{i^{1/2}}\right)^4 \sim 10^{-4},
\end{equation}     
with $T_{RH_{E1}}/T_{RH}$ being the ratio of the reheat temperatures of the 1st exotic sector and our own sector ($0.06$ in standard $N$naturalness with $r = 1$).  This sum is dominated by $i=1$, the sector with the lowest Higgs mass (and thus the most energy density) gives us a contribution of $\mathcal{O} (10^{-4})$ to $\Delta N_{eff}$. Evolving the sectors thermal histories forward in time to the recombination era gives us a slightly larger value, but still of order $\mathcal{O}(10^{-4})$, well below current CMB bounds. 
It should be noted that modifying the exotic sectors' structure (e.g. adjusting the exotic sectors to have a lower Higgs mass squared or clustering multiple hidden sectors close to the first exotic one) leads to a $\Delta N_{eff}$ contribution that is larger than the base $N$naturalness case. This increase is typically not excluded by current bounds, indicating a large degree of liberty in the structure and number of exotic hidden sectors.

@@

The generalization of possible reheating mechanisms mentioned in section~\ref{sec:reheat} --- where the reheating mechanism no longer depends on the Higgs' mass parameter of a given sector --- opens up a wide range of hidden sectors for study. Specifically, this allows mirror sectors with large Higgs vevs to be reheated to significant energy densities and thus produce gravitational waves with enough power to be detected. Crucially, despite this analysis being limited to mirror sectors with large Higgs masses, this analysis pertains to any strong, confining phase transition at high scales.
Since $N_{eff}$ constraints remain our strongest cosmological bounds for massive standard sectors, our starting point for exploring the limits of high transition temperatures is Eq.~(\ref{eqn:DeltaNeff}). Assuming heavy, standard sectors (with the only relativistic particles being photons and neutrinos) we can saturate the bounds of Eq.~(\ref{eqn:neffBounds}) and solve for the maximum temperature allowed for any number of sectors:
\begin{equation}\label{eqn:energyDensityAllowed}
\begin{split}
T_i &\sim 0.38 \,T_{SM} \,\,\,\,\, \mathrm{1}\,\, \mathrm{hidden}\,\, \mathrm{sector},
\\
T_i &\sim 0.25 \,T_{SM} \,\,\,\,\, \mathrm{5} \,\,\mathrm{hidden}\,\, \mathrm{sectors},
\\
T_i &\sim 0.21 \,T_{SM} \,\,\,\,\, \mathrm{10} \,\,\mathrm{hidden}\,\, \mathrm{sectors},
\\
T_i &\sim 0.12 \,T_{SM} \,\,\,\,\, \mathrm{100} \,\,\mathrm{hidden}\,\, \mathrm{sectors},
\end{split}
\end{equation}
where all the hidden sectors have the same temperature as one another.

Using these restrictions, we can examine the behaviour of standard sectors with a much larger vev than our own. In terms of the $N$naturalness framework, this means we can get an SFOPT for QCD if we look at sectors with $i$ greater than the critical index of Eq.~(\ref{eqn:critIndex}) where all the quark masses are above the QCD confinement scale, as long as their temperatures are below the bounds presented here. 
 %of looking at various different sectors above the critical index, as mentioned in Sec.~\ref{sec:dQCD}. The signals for both the maximal case ($10^{16}$ limit) and several other high transition temperatures (involving sectors $i > 10^{10}$) scenarios are shown in Sec.~\ref{sec:gw}. \textcolor{yellow}{This assumes that only photons and neutrinos are relativistic? Yes.}

@@

\section*{Acknowledgements}
